---
output:
  github_document:
    html_preview: false
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a package that provides functions to cope with binomial distribution.

* `bin_variable()` shows a list of binomial variables (of class `"binvar"`)
* `bin_choose()` calculate the number of possible outcomes given binomial variables
* `bin_mean()` `bin_mode()`, etc. calculate the summary statistics of given binomial experiment
* `bin_probability()` calculate probability of a specific number of success
* `bin_distribution()` show a dataframe of probability distribution(of class `"bindis"`)
* `plot()` method for a `"bindis"` object to graph probability distribution
* `bin_cumulative()` show a dataframe of cumulative probability (of class `"bincum"`)
* `plot()` method for a `"bincum"` object to graph cumulative probability 


## Motivation

This package has been developed to make binomial operations easier.


## Usage

```{r}
library(binomial)
#set up binomial variables and get summary statistics
variables = bin_variable(trials = 2,prob = .5)
variables
summary(variables)
# calculate specific statistic measurement
bin_variance(trials = 2,prob = .5)
bin_mean(trials = 2,prob = .5)
bin_mode(trials = 2,prob = .5)
bin_skewness(trials = 2,prob = .5)
bin_kurtosis(trials = 2,prob = .5)
#calculate number of possibile outcomes
bin_choose(n = 5, k = 2)
#calculate probability of getting a specific number of success
bin_probability(1,2,.5)
# given trilas and probability, show probability distribution and its plot
dis = bin_distribution(2,.5)
dis
plot(dis)
# given trilas and probability, show cumulative probability and its plot
cum = bin_cumulative(2,.5)
cum
plot(cum)
```