---
title: "Getting Started with binomial"
author: "YU JI"
date: "2019.04.30"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r }

library(binomial)
```

## Binomial

The package `"binomial"` provide a set of functions about caculating binomial probability, some statistics like mode, skewness and kurtosis, and display lists of probability or cumulative probability for given trials and probability of success.


## Setting up binomial variables

Use the function `bin_variable()`, and the generated type can be printed in a specific format; use function `summary()` to the generate virable to get some statistic summary in a clear and neat format:

```{r}
variables = bin_variable(trials = 2,prob = .5)
variables
summary(variables)
```

## Get statistic summary measures using functions `bin_variance()`, `bin_mean()`,`bin_mode()`,`bin_skewness()`,`bin_kurtosis()`,

```{r}
bin_variance(trials = 2,prob = .5)
bin_mean(trials = 2,prob = .5)
bin_mode(trials = 2,prob = .5)
bin_skewness(trials = 2,prob = .5)
bin_kurtosis(trials = 2,prob = .5)
```


## Calculate how many possible outcomes there are for given binomial variables

Use function `bin_choose()` to calculate possible outcomes of given number of trials, success:

```{r}
bin_choose(n = 5, k = 2)
```

## Getting binomial distribution and probabilities:

Use function `bin_prbability()` to get the probability of desired times of successes given total trials and probability of success

```{r}
bin_probability(1,2,.5)
```

Use `bin_distribution()` to get a dataframe of the probability of all number of successes and use `plot()` to visualize it:
```{r}
dis = bin_distribution(2,.5)
dis
plot(dis)
```


Use `bin_cumulative()` to get the cumulative probability of getting all possible number of success and use `plot()` to visualize it:
```{r}
cum = bin_cumulative(2,.5)
cum
plot(cum)
```

